opXRD: Open Experimental Powder X-ray Diffraction Database

### 2024-07-05 main.tex
Corrected sutter-fella affiliation

\author[1,2]{Daniel Hollarek}
\author[1,2]{Henrik Schopmans}
\author[1,2]{Jona Östreicher}
\author[2]{Simon Schweidler}
\author[3]{Adie Alwen}
\author[4]{Mriganka Singh}
\author[4]{Tim Kodalle}
\author[2]{Ben Breitung}
\author[4]{Maged Abdelsamie}
\author[4,5]{Carolin Sutter-Fella}
\author[3]{Andrea Hodge}
\author[1,2]{Pascal Friederich}

@@

\affil[1]{Institute of Theoretical Informatics, Karlsruhe Institute of Technology,\protect \\
Kaiserstr. 12, 76131 Karlsruhe, Germany}
\affil[2]{Institute of Nanotechnology, Karlsruhe Institute of Technology,\protect \\ Kaiserstr. 12, 76131 Karlsruhe, Germany}
\affil[3]{Department of Aerospace and Mechanical Engineering, University of Southern California, \protect \\3650 McClintock Ave, Los Angeles, CA 90089, USA}
\affil[4]{Department of Chemical Engineering and Materials Science, University of Southern California,\protect \\ 925 Bloom Walk, HED 216, Los Angeles, CA 90089, USA}
\affil[5]{Lawrence Berkeley National Laboratory, Molecular Foundry Division,\protect \\ 1 Cyclotron Rd., Berkeley, 94720 CA, USA}

>>>>

\author[1,2]{Daniel Hollarek}
\author[1,2]{Henrik Schopmans}
\author[1,2]{Jona Östreicher}
\author[2]{Simon Schweidler}
\author[3]{Adie Alwen}
\author[4]{Mriganka Singh}
\author[4]{Tim Kodalle}
\author[2]{Ben Breitung}
\author[4]{Maged Abdelsamie}
\author[4]{Carolin Sutter-Fella}
\author[3]{Andrea Hodge}
\author[1,2]{Pascal Friederich}

@@

\affil[1]{Institute of Theoretical Informatics, Karlsruhe Institute of Technology,\protect \\
Kaiserstr. 12, 76131 Karlsruhe, Germany}
\affil[2]{Institute of Nanotechnology, Karlsruhe Institute of Technology,\protect \\ Kaiserstr. 12, 76131 Karlsruhe, Germany}
\affil[3]{Department of Chemical Engineering and Materials Science, University of Southern California,\protect \\ 925 Bloom Walk, HED 216, Los Angeles, CA 90089, USA}
\affil[4]{Lawrence Berkeley National Laboratory, Molecular Foundry Division,\protect \\ 1 Cyclotron Rd., Berkeley, 94720 CA, USA}
